First Order Alternation

### 2018-09-20 quantifiers/draft.tex
ok

\comment[ri]{*** I am here ***}

\subsection{Coverage}

Assuming that the data domain is countable, the set of finite words
$\Sigma[X]^*$ is countable and the emptiness problem is recursively
enumerable. Moreover, by Lemma \ref{lemma:acceptance}, a systematic
enumeration of sequences of input events $\alpha \in \Sigma^*$ will
eventually discover an accepted word, provided that all path formulae
$\pathform{\alpha}$ belong to a decidable first-order theory.

However, if the automaton is empty, the enumeration of input event
sequences will fail to terminate, in general. The classical way to
fight this divergence problem is to consider a \emph{coverage} partial
order, which is a subset of the following relation:

\begin{definition}\label{def:coverage}
  Given an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$ and
  $S_1, S_2 \subseteq \bigcup_{q \in Q} \set{q(d_1,\ldots,d_{\#(q)})
    \mid d_1,\ldots,d_{\#(q)} \in \Data}$, we have $S_1 \sqsubseteq
  S_2$ if and only if 
  \begin{equation}\label{eq:po}
    \text{
      \begin{minipage}{0.7\textwidth}
        $\A$ accepts a word $w$ when started in a set of cubes $C_1
        \in S_1$ only if $\A$ accepts $w$ when started in a set of
        cubes $C_2 \in S_2$.
    \end{minipage}} 
  \end{equation}
\end{definition}
Since, in general the $\sqsubseteq$ relation is not definable using
available decidable (SMT) theories, we consider the following stronger
relation: $S_1 \supsetforex S_2$ if and only if, for each set of cubes
$C_1 \in S_1$, there exists a set of cubes $C_2 \in S_2$ such that
$C_1 \supseteq C_2$.

\begin{lemma}\label{lemma:coverage}
  Given an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$, for any
  sets of cubes $S_1, S_2 \subseteq \bigcup_{q \in Q}
  \set{q(d_1,\ldots,d_{\#(q)}) \mid d_1,\ldots,d_{\#(q)} \in \Data}$
  such that $S_1 \supsetforex S_2$, we have $S_1 \sqsubseteq S_2$.
\end{lemma}
\proof{  
\qed}

\subsection{Lazy Annotation}

>>>>

%% \subsection{Coverage}

%% Assuming that the data domain is countable, the set of finite words
%% $\Sigma[X]^*$ is countable and the emptiness problem is recursively
%% enumerable. Moreover, by Lemma \ref{lemma:acceptance}, a systematic
%% enumeration of sequences of input events $\alpha \in \Sigma^*$ will
%% eventually discover an accepted word, provided that all path formulae
%% $\pathform{\alpha}$ belong to a decidable first-order theory.

%% However, if the automaton is empty, the enumeration of input event
%% sequences will fail to terminate, in general. The classical way to
%% fight this divergence problem is to consider a \emph{coverage} partial
%% order, which is a subset of the following relation:

%% \begin{definition}\label{def:coverage}
%%   Given an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$ and
%%   $S_1, S_2 \subseteq \bigcup_{q \in Q} \set{q(d_1,\ldots,d_{\#(q)})
%%     \mid d_1,\ldots,d_{\#(q)} \in \Data}$, we have $S_1 \sqsubseteq
%%   S_2$ if and only if 
%%   \begin{equation}\label{eq:po}
%%     \text{
%%       \begin{minipage}{0.7\textwidth}
%%         $\A$ accepts a word $w$ when started in a set of cubes $C_1
%%         \in S_1$ only if $\A$ accepts $w$ when started in a set of
%%         cubes $C_2 \in S_2$.
%%     \end{minipage}} 
%%   \end{equation}
%% \end{definition}
%% Since, in general the $\sqsubseteq$ relation is not definable using
%% available decidable (SMT) theories, we consider the following stronger
%% relation: $S_1 \supsetforex S_2$ if and only if, for each set of cubes
%% $C_1 \in S_1$, there exists a set of cubes $C_2 \in S_2$ such that
%% $C_1 \supseteq C_2$.

%% \begin{lemma}\label{lemma:coverage}
%%   Given an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$, for any
%%   sets of cubes $S_1, S_2 \subseteq \bigcup_{q \in Q}
%%   \set{q(d_1,\ldots,d_{\#(q)}) \mid d_1,\ldots,d_{\#(q)} \in \Data}$
%%   such that $S_1 \supsetforex S_2$, we have $S_1 \sqsubseteq S_2$.
%% \end{lemma}
%% \proof{  
%% \qed}
